---
title: "CS 555 term project"
output: html_document
date: "2023-03-27"
---
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(stats)
library(car)
```
```{r}
airbnb <- read.csv('Aemf1.csv')
airbnb <- airbnb[airbnb$City =='Amsterdam',]
```

```{r}
set.seed(123) 
sample_indices <- sample(nrow(airbnb), size = 1000, replace = FALSE)
airbnb <- airbnb[sample_indices, ]
```

```{r}
airbnb <- airbnb[,-c(1,5,6,9,10)]
```

```{r}
airbnb$Weekday <- ifelse(airbnb$Day=='Weekday', 1, 0)
airbnb$Private <- ifelse(airbnb$Room.Type=='Private room', 1,0)
airbnb$Super_host <- ifelse(airbnb$Superhost=='True',1,0)
```

```{r}
airbnb <- airbnb[,-c(2,3,5)]
```

# Summary of Guest Satisfaction
```{r}
GuestWeekday <- airbnb$Guest.Satisfaction[airbnb$Weekday==1]
GuestWeekend <- airbnb$Guest.Satisfaction[airbnb$Weekday==0]
summary(GuestWeekday)
summary(GuestWeekend)
```
# simple t-test of Weekday and Weekend with 95% CI(Guest Satisfaction)
```{r}
t.test(GuestWeekday, mu=96, alternative = 'two.sided',conf.level = 0.95)
```
The null hypothesis being tested is whether the population mean of the variable GuestWeekday is equal to 96. The alternative hypothesis is two-sided, meaning that it tests whether the population mean is not equal to 96.
The sample mean of GuestWeekday is 94.15, and the 95% confidence interval for the population mean is (93.57692, 94.72176). The p-value is 4.612e-10, which is smaller than the significance level of 0.05, so we reject the null hypothesis. This means that there is enough evidence to conclude that the population mean of GuestWeekday is different from 96 at a 95% confidence level.
```{r}
t.test(GuestWeekend, mu=96, alternative = 'two.sided',conf.level = 0.95)
```
The null hypothesis being tested is whether the population mean of the variable GuestWeekend is equal to 96. The alternative hypothesis is two-sided, meaning that it tests whether the population mean is not equal to 96.
The sample mean of GuestWeekend is 94.52, and the 95% confidence interval for the population mean is (93.84512, 95.18673). The p-value is 1.69e-05, which is smaller than the significance level of 0.05, so we reject the null hypothesis. This means that there is enough evidence to conclude that the population mean of GuestWeekend is different from 96 at a 95% confidence level.
# two sample t-test of Weekday and Weekend (Guest Satisfaction)
```{r}
t.test(GuestWeekday, GuestWeekend, alternative = 'two.sided',conf.level = 0.95)
```
The null hypothesis being tested is whether there is no difference between the means of the two populations represented by GuestWeekday and GuestWeekend. The alternative hypothesis is two-sided, meaning that it tests whether the true difference in means is not equal to 0.
The sample means for GuestWeekday and GuestWeekend are 94.15 and 94.52, respectively. The 95% confidence interval for the difference in means is (-1.2473798, 0.5142094). The p-value is 0.4143, which is greater than the significance level of 0.05, so we fail to reject the null hypothesis. This means that there is not enough evidence to conclude that there is a significant difference between the means of GuestWeekday and GuestWeekend at a 95% confidence level.
# Summary of Cleaning Rating
```{r}
CleanWeekday <- airbnb$Cleanliness.Rating[airbnb$Weekday==1]
CleanWeekend <- airbnb$Cleanliness.Rating[airbnb$Weekday==0]
summary(CleanWeekday)
summary(CleanWeekend)
```
# simple t-test of Weekday and Weekend with 95% CI(Cleaning Rating)
```{r}
t.test(CleanWeekday, mu=10, alternative = 'two.sided',conf.level = 0.95)
```
The null hypothesis being tested is whether the population mean of the variable CleanWeekday is equal to 10. The alternative hypothesis is two-sided, meaning that it tests whether the population mean is not equal to 10.
The sample mean of CleanWeekday is 9.47, and the 95% confidence interval for the population mean is (9.405548, 9.543412). The p-value is 2.2e-16, which is smaller than the significance level of 0.05, so we reject the null hypothesis. This means that there is enough evidence to conclude that the population mean of CleanWeekday is different from 10 at a 95% confidence level.
```{r}
t.test(CleanWeekend, mu=10, alternative = 'two.sided',conf.level = 0.95)
```
The null hypothesis being tested is whether the population mean of the variable CleanWeekend is equal to 10. The alternative hypothesis is two-sided, meaning that it tests whether the population mean is not equal to 10.
The sample mean of CleanWeekend is 9.447983, and the 95% confidence interval for the population mean is (9.369796, 9.526171). The p-value is 2.2e-16, which is smaller than the significance level of 0.05, so we reject the null hypothesis. This means that there is enough evidence to conclude that the population mean of CleanWeekend is different from 10 at a 95% confidence level.

# two sample t-test of Weekday and Weekend (Cleaning Rating)
```{r}
t.test(CleanWeekday, CleanWeekend, alternative = 'two.sided',conf.level = 0.95)
```
The null hypothesis being tested is whether the population mean of the variable CleanWeekday is equal to the population mean of the variable CleanWeekend. The alternative hypothesis is two-sided, meaning that it tests whether the population mean of CleanWeekday is not equal to the population mean of CleanWeekend.
The sample means of CleanWeekday and CleanWeekend are 9.474480 and 9.447983, respectively. The 95% confidence interval for the difference in population means is (-0.07761258, 0.13060685). The p-value is 0.6176, which is greater than the significance level of 0.05, so we fail to reject the null hypothesis. This means that there is not enough evidence to conclude that the population mean of CleanWeekday is different from the population mean of CleanWeekend at a 95% confidence level.

# simple linear regression of price and guest
```{r}
fit_guest <- lm(Price~Guest.Satisfaction, data = airbnb)
summary(fit_guest)
```
The linear regression model in the code above examines the relationship between the Price variable (dependent variable) and the Guest.Satisfaction variable (independent variable) in the airbnb dataset. The lm() function fits a linear model and returns the model summary using the summary() function.

The model output shows the coefficients, the standard errors, and t-values for the intercept and Guest.Satisfaction. The coefficient for Guest.Satisfaction is 10.430, indicating that a unit increase in Guest.Satisfaction is associated with a $10.43 increase in Price. The p-value for the coefficient is < 0.001, indicating that the association between Guest.Satisfaction and Price is statistically significant. The R-squared value is 0.021, indicating that only 2.1% of the variance in Price is explained by Guest.Satisfaction.
```{r}
res_guest <- residuals(fit_guest)
pred_guest <- predict(fit_guest)
plot(x = pred_guest, y = res_guest, 
     xlab = "Predicted Value", ylab = "Residuals Value",
     main = "Residual Plot")
```
```{r}
anova(fit_guest)
```
In this case, the ANOVA table shows that the variation in the dependent variable (Airbnb Price) can be explained by the variation in the independent variable (Guest Satisfaction) with a high degree of statistical significance (F-value=21.568, p-value=3.872e-06). This indicates that Guest Satisfaction is a significant predictor of Airbnb Price.The results suggest that Guest Satisfaction is a significant predictor of Airbnb Price, while other variables may not be significant predictors.

# simple linear regression of price and cleaness
```{r}
fit_clean <- lm(Price~Cleanliness.Rating, data = airbnb)
summary(fit_clean)
```
In this linear regression model, we are trying to predict the price of an Airbnb listing based on its cleanliness rating. The model shows that there is a positive relationship between cleanliness rating and price, with a coefficient estimate of 30.70. However, this relationship is not statistically significant at the 0.05 level since the p-value is 0.1092. The R-squared value is very low, indicating that the model does not explain much of the variation in the data. Overall, this model does not provide strong evidence for a relationship between cleanliness rating and price.

```{r}
res_clean <- residuals(fit_clean)
pred_clean <- predict(fit_clean)
plot(x = pred_clean, y = res_clean, 
     xlab = "Predicted Value", ylab = "Residuals Value",
     main = "Residual Plot")
```
```{r}
anova(fit_clean)
```
Based on the ANOVA table, the p-value for the Cleanliness.Rating predictor variable is 0.1092, which means that it is not statistically significant at the 0.05 level of significance. This suggests that there is no evidence to suggest that the cleanliness rating of an Airbnb listing has a significant impact on its price. The sum of squares for the residuals is 254124890, indicating that there is still a significant amount of unexplained variability in the model. In this specific case, the F-value of 2.5703 and p-value of 0.1092 for the Cleanliness.Rating variable suggest that there is not a significant difference in the mean price across different cleanliness ratings.

# Multilinear Regression(Guest Satisfaction) 
```{r}
model <- lm(Guest.Satisfaction ~ ., data = airbnb)
summary(model)
```
In this model, the intercept is 45.27. The coefficients for the other independent variables indicate the change in Guest.Satisfaction associated with a one-unit increase in each variable, holding all other variables constant.

Based on the coefficient estimates and p-values, we can see that the following variables are statistically significant: Intercept,
Cleanliness Rating, Private, Super_host, City.Center..km., and Metro.Distance..km. 

The following variables are not statistically significant: Price, Person.Capacity, Bedrooms, Attraction.Index and Normalized.Attraction.Index, Restaurant.Index and Normalized.Restaurant.Index, and Weekday.

The last part of the output provides some additional statistics, including the residual standard error, the multiple R-squared, the adjusted R-squared, and the F-statistic. In this case, the model explains 46.34% of the variance in Guest.Satisfaction, and the F-statistic indicates that the model is significant at the p < .001 level.
```{r}
anova(model)
```
```{r}
Anova(model, type = 3)
```
The F-values and p-values for each predictor variable indicate whether or not that variable has a significant effect on the guest satisfaction. The predictor variables with low p-values (p < 0.05) are considered statistically significant, meaning that they have a significant effect on guest satisfaction. In this case, the predictor variables "Intercept", "Cleanliness.Rating", "City.Center..km.", "Metro.Distance..km.", "Private", and "Super_host" have p-values less than 0.05, indicating that they have a significant effect on guest satisfaction.

The overall result of this ANOVA table suggests that the combination of these five predictor variables together is a significant predictor of guest satisfaction on Airbnb.
```{r}
confint(model,level = 0.95)
```
```{r}
glm_model <- glm(Guest.Satisfaction ~ .,data = airbnb)

summary(glm_model)
```
The coefficients indicate the expected change in guest satisfaction for a one-unit increase in the corresponding predictor variable while holding other predictors constant. For example, a one-unit increase in the cleanliness rating is associated with an increase in guest satisfaction by 5.4 on average.

The p-values associated with the coefficients can be used to assess the statistical significance of each predictor in predicting guest satisfaction. Here, only the predictors Intercept, Cleanliness.Rating, City.Center..km., Metro.Distance..km., Private, Super_host have p-values less than 0.05, which suggests that they are statistically significant predictors of guest satisfaction.

The residual deviance is 26587 on 986 degrees of freedom, and the AIC is 6148.3. These values can be used to assess the goodness of fit of the model. Lower values of deviance and AIC indicate a better fit of the model to the data.
```{r}
anova(glm_model)
```
In this specific example, we are modeling the response variable Guest.Satisfaction and adding 5 predictor variables sequentially. The first model includes no predictor variables (NULL), and subsequent models include one additional predictor variable at a time. As each variable is added to the model, the deviance decreases, indicating that the model is becoming a better fit to the data. The most important variable appears to be airbnb$Cleanliness.Rating as it is associated with the largest drop in deviance.

# Mutiple Linear Regression(Price)
```{r}
model2 <- lm(Price~., data = airbnb)
summary(model2)
```
The outcome of the linear regression analysis shows that the model is significant (p-value < 2.2e-16) and explains approximately 36% of the variance in the dependent variable, Price.

The coefficients of the independent variables show that Person.Capacity, Bedrooms, and Private have a statistically significant positive effect on Price, while City.Center..km. has a significant negative effect on Price. Cleanliness.Rating, Guest.Satisfaction, Metro.Distance..km., Attraction.Index, Normalised.Attraction.Index, Restraunt.Index, Normalised.Restraunt.Index, Weekday, and Super_host do not have a significant effect on Price.

The intercept, -249.0140, represents the expected Price of an Airbnb listing with all independent variables held at 0.

Overall, the results suggest that Person Capacity, Bedrooms, City.Center..km., Private appear to have a significant effect of Airbnb Price.

The multiple R-squared value indicates that the predictor variables explain 35.9% of the variance in the response variable.
```{r}
anova(model2)
```
The null hypothesis for each variable is that the variable has no effect on the response variable (airbnb$Price). The p-value for each variable indicates the probability of observing a result as extreme as the one in the sample if the null hypothesis were true. A p-value less than 0.05 is generally considered statistically significant, indicating that we can reject the null hypothesis and conclude that the variable has a significant effect on the response variable.

In this case, we can see that several variables have a statistically significant effect on Price, including Person.Capacity, Cleanliness.Rating, Guest.Satisfaction, Bedrooms, City.Center..km., Normalised.Attraction.Index, and Private. Other variables, such as Metro.Distance..km., Attraction.Index, Restraunt.Index, Normalised.Restraunt.Index, Weekday, and Super_host do not have a significant effect on airbnb$Price.

The regression model can be used to predict the value of airbnb$Price based on the values of the significant predictor variables.
```{r}
confint(model2)
```
```{r}
Price_glm <- glm(Price~.,data = airbnb)
summary(Price_glm)
```
This is a multiple linear regression model that predicts the price of an Airbnb rental based on various predictors.

The coefficients table shows the estimated effect of each predictor on the price of the rental. The intercept term represents the predicted price when all predictors are zero.

Based on the p-values, we can see that several predictors are statistically significant at the 5% significance level. These include Person.Capacity, Bedrooms, City.Center..km., and Private.

However, other predictors such as Cleanliness.Rating, Guest.Satisfaction, Metro.Distance..km., Attraction.Index, Normalised.Attraction.Index, Restraunt.Index, Normalised.Restraunt.Index, Weekday, and Super_host are not statistically significant, meaning that they do not have a significant effect on the price of an Airbnb rental.

The model's overall performance can be assessed by the deviance measures, which indicate the difference between the observed response values and the predicted values. The null deviance represents the total variability in the response variable, while the residual deviance represents the variability that cannot be explained by the model. A lower residual deviance indicates a better fit of the model to the data. In this case, the residual deviance is substantially lower than the null deviance, indicating that the model explains a significant amount of variability in the response variable.

The AIC value of 14871 indicates that this model is not a very good fit to the data, as a lower AIC value is preferred. It may be necessary to consider additional predictors or transformations of the existing predictors to improve the model's performance.
```{r}
anova(Price_glm)
```
The table shows that the addition of each predictor variable results in a significant decrease in deviance, which indicates that each variable contributes significantly to explaining the variation in the response variable (airbnb price).
```{r}
Anova(model2, type = 3)
```









